---
title: "MATH 216 Homework 4"
author: "Brenda Li"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    smooth_scroll: false
---

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4.5}
# Suggested packages; feel free to use more!
library(tidyverse)
library(USAboundaries)
library(maptools)
library(sp)
library(broom)
library(rvest)
library(stringr)
library(rgdal)
library(rgeos)

#Census Data
census <- read_csv(file="Employment.csv") 
census<-select(census,SE_T001_001,SE_T002_002,Geo_FIPS,Geo_NAME) %>% 
  rename(Pop=SE_T001_001,Pop_Density=SE_T002_002)

#Getting counties shape data
states_shp<-us_counties()
states_data <- states_shp@data 
states_polygon <- tidy(states_shp, region="geoid")

```



## Admistrative:

Please indicate

* Who you collaborated with: Bianca G, Shannia F,
* Roughly how much time you spent on this HW so far: 6 hours
* The URL of the RPubs published URL [here](http://rpubs.com/brendali121/HW4).
* What gave you the most trouble: Figuring out how to get the data from the Amazon webpage the way I wanted.
* Any comments you have:



## Question 1:

**Question**:  DHL, a German shipping company, has a ton of money to build a
shipping hub in the United States. Where should they build it?

**Deliverable**: A choropleth map of the lower 48 states (no Puerto Rico) where
the color corresponds to the distance of the given area to the shipping hub,
which is marked on the map with a large red dot.

### Method 1: Amazon Fulfillment Centers

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4.5}
#Getting a dataframe of the location of Amazon fulfilment centers
url<-'https://trustfile.avalara.com/resources/amazon-warehouse-locations/'
webpage<-read_html(url)
amazon_table <- html_nodes(webpage, 'table')
amazon<- html_table(amazon_table)
fulfillment<-do.call("rbind",amazon)


#Determining which county has the greatest number of fulfillment centers
fulfillment %>% 
  group_by(County) %>% 
  summarise(n=n()) %>% 
  arrange(desc(n)) %>% 
  rename("Number of Fulfillment Centers"=n) %>% 
  head()


#Determining which of the counties with many fulfilment centers has the largest population
amazon_census<-census %>% 
  filter(str_detect(Geo_NAME,"Maricopa")|str_detect(Geo_NAME,"Boone")|
           str_detect(Geo_NAME,"Bullitt")|
           str_detect(Geo_NAME,"Cumberland")|
           str_detect(Geo_NAME,"New Castle")|
           str_detect(Geo_NAME,"Clarke"))

census %>%
  arrange(desc(Pop))


#Coordinates for Phoenix, AZ
plong<--112.0740
plat<-33.4484

```

In choosing where to place the shipping hub, I decided to look at the location of Amazon fulfillment centers so I could place the hub in a county with a high number of these centers since Amazon will have to rely on a shipping service in order to get their products out to customers (I'm operating under the assumption that Amazon doesn't have an exclusive contract with another shipping company already).  I found a webpage with tables of the location of fulfillment centers in each state, and downloaded them into R so that I could look at which counties had the most fulfillment centers.  Then, I used census data to look at the populations of the counties with the highest number of fulfilment centers, because I also wanted to place the shipping hub in  heavily populated area, which would have a high demand for shipping services. Thus, Maricopa County of Arizona turned out to be a county with a high number of Amazon fulfilment centers as well as a large population, so I chose to place the shipping hub there. The major city in Maricopa County is Phoenix, so that's where I placed the hub in order to capitalize also on the proximity to a major airport.

### Method 2: Center of Mass

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4.5}
#Getting centroid data
centroids <- coordinates(states_shp)

  
#Combining counties+centroid+census data
combined<-cbind(states_data,centroids) %>% 
  filter(!state_name %in% c("Alaska", "Hawaii", "Puerto Rico")) %>% 
  mutate(fips=as.integer(geoid)) %>% 
  left_join(census,by=c("fips"="Geo_FIPS")) 

colnames(combined)[11] <- "x"
colnames(combined)[12] <- "y"
combined[2290,14]=1142234 #for Fairfax County Virginia


#Calculating Center of Mass
combined<- combined %>% 
  mutate(xm=x*Pop) %>% 
  mutate(ym=y*Pop)

xcoord<-sum(combined$xm)/sum(combined$Pop)
ycoord<-sum(combined$ym)/sum(combined$Pop)

xcoord
ycoord

```

### Plots
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4.5}

#Synthesizing States Data with Distances
states <- left_join(states_polygon, states_data, by=c("id"="geoid")) %>% 
  mutate(distance=sqrt((long-xcoord)^2+(lat-ycoord)^2)) %>%
  mutate(amazon_dist=sqrt((long-plong)^2+(lat-plat)^2)) %>% 
  filter(!state_name %in% c("Alaska", "Hawaii", "Puerto Rico"))


#Plots
amazon_plot<- ggplot(data=states, aes(x=long, y=lat, group=group, fill=amazon_dist)) +
  geom_polygon() +
  scale_fill_gradient(low="white", high="darkgreen") + 
  geom_path(size=0.1) +
  annotate("point", x=plong, y=plat, col="red", size=5) +
  coord_map()+
  labs(title="Choropleth Map with Center Found through Looking at Amazon Warehouses")
amazon_plot

centroid_plot<- ggplot(data=states, aes(x=long, y=lat, group=group, fill=distance)) +
  geom_polygon() +
  scale_fill_gradient(low="white", high="darkgreen") + 
  geom_path(size=0.1) +
  annotate("point", x=xcoord, y=ycoord, col="red", size=5) +
  coord_map()+
  labs(title="Choropleth Map with Center Found Using Center-of-Mass Method")
centroid_plot

```





